---
title: "R Markdown and Leaflet Project"
author: "samaa essa"
date: "12/12/2020"
output: html_document
---

## Task Description

Host a webpage on either GitHub Pages, RPubs, or NeoCities.

The webpage must contain the date that webpage is created, and it must contain a map created with Leaflet.

### Load Data
I choose dataset about the best restaurants in the world. By Megh Mayur. Contains the list of The World’s 50 Best Restaurants for 2018. it could be accessed from [here](https://www.kaggle.com/mmayur/the-worlds-50-best-restaurants).
```{r}
data <- read.csv("/home/samaaessa/Desktop/DS coursera/course 9/The Worlds 50 Best Restaurants 2018.csv")
```

### Library Needed
```{r, echo=FALSE}
library(leaflet)
library(htmltools)
```

### Map creation
```{r}
map <- data %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(popup=paste
             ("<br>Country: ", 
               htmlEscape(data$Country), 
              "<br>City: ", 
               htmlEscape(data$City), 
              "<br>Restaurant: ", 
               htmlEscape(data$Name),
              "<br>Ranking: ",
               formatC(data$Ranking, format = "d", big.mark = ",")
              ) 
            )
map
```

